\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}

\usepackage{url}

\title{RetroBlue: Bluetooth Rotary Phone\\ES50 Project Proposal}
\author{Michaels Tingley and Traver, and Kyle Solan\\\url{{michaeltingley, mtraver, ksolan}@college.harvard.edu}}
\date{April 5, 2014}

\begin{document}
    \maketitle

    \section{Our Project}
    We plan to turn a rotary phone into a hands-free Bluetooth device that can pair with a cell phone and make and receive calls. It will behave exactly like a rotary phone plugged into an ordinary phone jack, except that calls are routed through a cell phone instead of a land line. Specifically, our phone will have the following functionality:

    \begin{description}
        \item[Bluetooth pairing.] Users will be able to pair their cell phone with the rotary phone.
        \item[Receiving calls.] When the user's cell phone receives a call, the rotary phone's original mechanical ringer will ring. The user will be able to simply pick up the handset to answer it.
        \item[Making calls.] To make a call, the user will be able to pick up the handset and dial a number on the phone's original dial. We will tap into the existing circuity/machanics of the dial to detect the number dialed, and forward it along to the Bluetooth hardware to make the call. If we have time, we will also make a fake dial tone for increased authenticity.
        \item[Display.] We would like to incorporate a small OLED screen that will display information such as pairing status and caller ID.
    \end{description}

    We think this project will be fun for the novelty factor, but we also think it will provide a good challenge and integrate several topics we've learned about in class. We will need to reverse-engineer the phone's rotor, handset, and ringer; connect these components to an Arduino; and program the Arduino to interface with a Bluetooth module.

    \section{Resources}


    \section{Schedule}


    \section{Diagram}


    \section{Team Management}


    \section{Scope and Required Knowledge}


    \section{Parts List}


\end{document}
